Versioned data: why it’s needed and how it can be achieved (easily and cheaply)

### 2017-08-03 ms.tex
pointing people where to see how to do use datastorr; leaving it outside of the ms allows the pkg to change as needed
Minor bug fixes

For example, \texttt{datastorr} was used to build the package \texttt{baad.data} (\smurl{github.com/dfalster/baad.data}), which is an interface to the Biomass and Allometry Database (BAAD) stored at \smurl{github.com/dfalster/baad}. \texttt{baad.data} consists of only a few simple functions, that were automatically generated (along with the associated help files) with \texttt{datastorr}. And importantly \texttt{baad.data} contains no actual data so is very quick to install and takes up virtually no space on the user's harddrive. When the function \texttt{baad.data::baad_data()} is called, the system will download the latest version; if there have not been any changes since the last time the function was called, it will simply retrieve the data from memory, making the system very efficient (and also allowing the system to work seamlessly if the computer is offline). If a researcher requires an older version of BAAD, perhaps to reproduce an analysis, specifying the version number of the data as an argument in \texttt{baad.data::baad_data()} will retrieve and store this, without overwriting any other dataset versions they may have previously downloaded.

Using \texttt{datastorr}, researchers can set up their own versioned database (and R package) simply by providing: 1) a github repository name (e.g., ``traitecoevo/taxonlookup''); 2) a single file that will contain the versioned data (e.g., ``taxonlookup.csv''); 3) and the function used to load this into \texttt{R} (e.g., \texttt{read.csv()}).

>>>>

For example, \texttt{datastorr} was used to build the package \texttt{baad.data} (\smurl{github.com/dfalster/baad.data}), which is an interface to the Biomass and Allometry Database (BAAD) stored at \smurl{github.com/dfalster/baad}. \texttt{baad.data} consists of only a few simple functions, that were automatically generated (along with the associated help files) with \texttt{datastorr}. And importantly \texttt{baad.data} contains no actual data so is very quick to install and takes up virtually no space on the user's harddrive. When the function \texttt{baad.data::baad\_data()} is called, the system will download the latest version; if there have not been any changes since the last time the function was called, it will simply retrieve the data from memory, making the system very efficient (and also allowing the system to work seamlessly if the computer is offline). If a researcher requires an older version of BAAD, perhaps to reproduce an analysis, specifying the version number of the data as an argument in \texttt{baad.data::baad\_data()} will retrieve and store this, without overwriting any other dataset versions they may have previously downloaded.

Using \texttt{datastorr}, researchers can set up their own versioned database (and R package) simply by providing: 1) a github repository name (e.g., ``traitecoevo/taxonlookup''); 2) a single file that will contain the versioned data (e.g., ``taxonlookup.csv''); 3) and the function used to load this into \texttt{R} (e.g., \texttt{read.csv()}). A tutorial explaining precisely how to set this up is available at \smurl{github.com/richfitz/datastorr}.
